The finite representation property for some reducts of relation algebras

### 2021-04-17 filtration-stuff/NewText.tex
New file with filtrations stuff

\author{Daniel Rogozin}
\date{}
\title{Notes on filtration of logics containing {\bf K5}}

\begin{document}

@@

\section{Preliminaries}

\begin{defin}
  A normal modal logic is a set of formulas that contains all Boolean tautologies,
  formulas $\Diamond p \lor \Diamond q \leftrightarrow \Diamond (p \lor q)$ and
  $\Diamond \bot \leftrightarrow \bot$, and is closed under Modus Ponens, Substitution, and
  Monotonicity:
  from $\varphi \rightarrow \psi$ infer $\Diamond \varphi \rightarrow \Diamond \psi$.
\end{defin}

\begin{defin} An Kripke model is a triple $\mathcal{M} = \langle W, R, \vartheta \rangle$,
  where $R \subseteq W \times W$, $\vartheta : \operatorname{PV} \to 2^W$, and
  the connectives have the following semantics:

  \begin{enumerate}
    \item $\mathcal{M}, w \models p \Leftrightarrow w \in \vartheta(p)$
    \item $\mathcal{M}, w \models \neg \varphi \Leftrightarrow \mathcal{M}, w \nvDash \varphi$
    \item $\mathcal{M}, w \models \varphi \lor \psi \Leftrightarrow \mathcal{M}, w \models \varphi \text{ or } \mathcal{M}, w \models \psi$
    \item $\mathcal{M}, w \models \Diamond \varphi \Leftrightarrow \exists v \in R(w) \: \mathcal{M}, v \models \varphi$
  \end{enumerate}
\end{defin}

\begin{defin}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a Kripke model.
  A Kripke model $\mathcal{M}' = \langle W', R', \vartheta' \rangle$ is a generated submodel of
  $\mathcal{M}$, where:
  \begin{enumerate}
    \item $\emptyset \neq W' \subseteq W$ and $W'$ is $R$-closed, i.e., for each $u \in W'$ and $v \in W$,
    $u R v$ implies $v \in W'$
    \item $R' = R \cap W' \times W'$
    \item for every propositional variable $p$, $\vartheta(p)' = \vartheta(p) \cap W'$
  \end{enumerate}
\end{defin}

\begin{fact}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a Kripke model and
  $\mathcal{M}' = \langle W', R', \vartheta' \rangle$ its generated submodel,
  then for each $w \in W'$
  \begin{center}
    $\mathcal{M}, w \models \varphi$ iff $\mathcal{M}', w \models \varphi$
  \end{center}
\end{fact}

By ${\bf K5}$ we mean the logic ${\bf K} \oplus {A5}$, where ${A5} = \Diamond p \to \Box \Diamond p$. It is known that ${\bf K5}$ is the modal logic of all Euclidean frames. A frame is called Euclidean if for each $x, y, z$, $x R y$ and $x R z$ implies $y R z$.

\begin{prop} \label{K5proves}
  ${\bf K5}$ proves
  \begin{enumerate}
    \item $\Box^3 p \leftrightarrow \Box^2 p$
    \item $\Box^2 \Diamond p \leftrightarrow \Box \Diamond p$
    \item $\Box \Diamond \Box p \leftrightarrow \Box \Box p$
    \item $\Box \Diamond^2 p \leftrightarrow \Box \Diamond p$
  \end{enumerate}
\end{prop}

\begin{prop} \label{k5useful}
  Let $\mathcal{M}$ be a ${\bf K}5$ model, $x R y$ for $x, y \in W$ then one has
  \begin{center}
    $\mathcal{M}, x \models \Box \Diamond \varphi$ iff $\mathcal{M}, y \models \Box \Diamond \varphi$.
  \end{center}
\end{prop}

  \begin{enumerate}
    \item Suppose $\mathcal{M}, x \models \Box \Diamond \varphi$. Then $\mathcal{M}, y \models \Diamond \varphi$ and $\mathcal{M}, y \models \Box \Diamond \varphi$
    \item Suppose $\mathcal{M}, y \models \Box \Diamond \varphi$, then $\mathcal{M}, x \models \Diamond \Box \Diamond \varphi$, so $\mathcal{M}, x \models \Box \Diamond \varphi$.
  \end{enumerate}
\end{proof}

\subsection{Filtrations: general definitions}

@@

\begin{enumerate}
  \item Let $\mathcal{L}$ be a complete normal modal logic. If $\operatorname{Frames}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property.
  \item If the class of models $\operatorname{Mod}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property and Kripke complete as well.
\end{enumerate}
\end{lemma}

\section{Filtration of Euclidean logics}

First of all, let us ensure that a minimal filtration of an Euclidean frame is not necessary Euclidean.
Let $[x] \sim_{\Gamma} [y]$ and $[x] \sim_{\Gamma} [z]$. Then for some $x' \in [x]$ $y' \in [y]$, one has
$x' R y'$ and $x'' R z'$ for some $x'' \in [x]$ and $z' \in [z]$. Clearly, we cannot claim that $x' = x''$ in general. Thus, minimal filtration does not preserve the required property.

\begin{lemma}
  ${\bf K5}$ admit filtration.
\end{lemma}

\begin{proof}
  Let $\mathcal{M}$ be a ${\bf K5}$-model and $\Gamma_0$ a finite set of formulas closed under subformulas.
  Let us put $\Gamma = \Gamma_0 \cup \operatorname{Sub}(\{ \Diamond \Box \psi \: | \: \Box \psi \in \Gamma_0 \}) \cup \Psi$, where $\Psi = \nabla_1 \nabla_2 \dots \nabla_n \Box \psi$ for $\Box \psi \in \Gamma_0$ and
  $\nabla_i \in \{ \Diamond, \Box \}$. By Proposition~\ref{K5proves}, any element of $\Phi$ has one of the four forms. Thus, $W \sim_{\equiv_{\Gamma}}$ has a finite index.
  We put $\widehat{R} = R^{\operatorname{max}}_{\Gamma}$.
\end{proof}

@@

  \xymatrix{
  &&&&&&& w_5\ar@(ul,ur) \ar@<-.5ex>[d] \\
  &&&&&& w_1\ar@(ul,ur)  & w_4 \ar@<.5ex>[u] \\
  &&&&&& w_2 \ar[u] & w_3 \ar[u]
  }
\end{proof}

@@

Let us also note that strict filtrations of this model is not Euclidean.
Suppose by contrary that $\widehat{R}^{\mathcal{E}}$ is a strict filtraction of that model. So $R_{min}^E \subseteq \widehat{R}^{\mathcal{E}}$, since $R_{min}^E$ is the minimal Euclidean relation containing $R_{min}$. On the other hand, $R_{min}^E \not\subseteq R_{max}$, so is not $\widehat{R}^{\mathcal{E}}$.
\section{Filtration for {\bf K4}}

\begin{prop}
  Let $R$ be a binary relation on $W \neq \emptyset$. Define $R^{+} = \bigcup \limits_{i < \omega} R_i$
  \begin{enumerate}
    \item $R_0 = R$
    \item $R_{n + 1} = R_n \circ R$
  \end{enumerate}
  Then $R^{+}$ is transitive
\end{prop}

\begin{lemma}
  Let $\mathcal{M} = \langle W, R, \vartheta \rangle$ be a transitive model and $\overline{\mathcal{M}} = \langle \overline{W}, \overline{R}, \overline{\vartheta} \rangle$ its minimal filtration through a finite $\operatorname{Sub}$-closed set of formulas $\Theta$.

  Then $\overline{\mathcal{M}}^{+} = \langle \overline{W}, (\overline{R})^{+}, \overline{\vartheta} \rangle$ is a $\Theta$-filtration of $\mathcal{M}$.
\end{lemma}

\begin{proof}
  $(\overline{R})^{+}$ obviously contains $R$. By the previous proposition, $(\overline{R})^{+}$ is transitive.
  Let us show that $(\overline{R})^{+} \subseteq R^{max}_{\Theta}$.

  Let $\hat{x}, \hat{y} \in \overline{W}$ with $\hat{x} (\overline{R})^{+} \hat{y}$ and
  $\Box \varphi \in \Theta$ with $\mathcal{M}, x \models \Box \varphi$. Let us show that $\mathcal{M}, y \models \varphi$.

  If $\hat{x} (\overline{R})^{+} \hat{y}$, then there exist equivalence classes $\hat{x}_1, \dots, \hat{x}_n$ such that
  \begin{center}
    $\hat{x} \overline{R} \hat{x}_1 \overline{R} \dots \overline{R} \hat{x}_n \overline{R} \hat{y}$
  \end{center}

  $\mathcal{M}, x \models \Box \varphi$ implies $\mathcal{M}, x \models \Box \Box \varphi$. Thus, $\overline{M}, \hat{x} \models \Box \Box \varphi$.

  $\hat{x} \overline{R} \hat{x}_1$, so there are $x_1 \in \hat{x}$ and $x_2 \in \hat{x}_1$ with $x_1 R x_2$. In particular, $\mathcal{M}, x_2 \models \Box \varphi$,
  so $\overline{\mathcal{M}}, \hat{x}_2 \models \Box \varphi$, and et cetera.

  For each $i \in \{1, \dots, n\}$ we have $\mathcal{M}, x_i \models \Box \varphi$ which is shown inductively:

  If $\mathcal{M}, x_i \models \Box \varphi$ for $x_i \in \hat{x}_i$, so $\mathcal{M}, x_i \models \Box \Box \varphi$, but there exist ${x_i}' \in \hat{x}_i$ and $x_{i + 1} \in \hat{x}_{i + 1}$, so
  $\mathcal{M}, x_{i + 1} \models \Box \varphi$.

  Finally, we have $\mathcal{M}, x_n \models \Box \varphi$ for $x_n \in \hat{x}_n$, but $\hat{x}_n \overline{R} \hat{y}$, so $\mathcal{M}, y' \models \varphi$ for each $y' \in \hat{y}$. Thus, $\varphi$ is true at $y$ as well.
\end{proof}

\begin{proof}
  Let $\hat{x}, \hat{y} \in \overline{W}$ with $\hat{x} (\overline{R})^{+} \hat{y}$ and
  $\Box \varphi \in \Theta$ with $\mathcal{M}, x \models \Box \varphi$. Let us show that $\mathcal{M}, y \models \varphi$.

  If $\hat{x} (\overline{R})^{+} \hat{y}$, then there exist equivalence classes $\hat{x}_1, \dots, \hat{x}_n$ such that
  \begin{center}
    $\hat{x} \overline{R} \hat{x}_1 \overline{R} \dots \overline{R} \hat{x}_n \overline{R} \hat{y}$
  \end{center}

  Let us show that $\mathcal{M}, \hat{x}_i \models \Box \varphi$ inductively:
  \begin{enumerate}
    \item $n = 1$
    We have the following sequence:
    \begin{center}
      $\hat{x} \overline{R} \hat{x}_1 \overline{R} \hat{y}$
    \end{center}
    $\hat{x} \overline{R} \hat{x}_1$, so there are $x' \in \hat{x}$ and $x_1' \in \hat{x}_1$ such that $x' R x_1'$. $\Box \varphi$ is true at $x'$, so is $\Box \Box \varphi$. Then
    $\mathcal{M}, x_1' \models \Box \varphi$ since $x_1' \in R(x')$.
    So $\overline{\mathcal{M}}, \hat{x}_1 \models \Box \varphi$.

    \item $n = i + 1$
    The case is the following:
    \begin{center}
      $\hat{x} \overline{R} \hat{x}_1 \overline{R} \dots \overline{R} \hat{x}_i \overline{R} \hat{x}_{i + 1} \overline{R} \hat{y}$
    \end{center}

    By IH, $\Box \varphi$ is true at $\hat{x}_i$, so is $\Box \Box \varphi$. Hence, we have $\overline{\mathcal{M}}, \hat{x}_{i + 1} \models \Box \varphi$ since
    $\hat{x}_i \overline{R} \hat{x}_{i + 1}$.
  \end{enumerate}

  That is, for each $0 < n < \omega$, if we have a sequence of equivalence classes with $\hat{x} \overline{R} \hat{x}_1 \overline{R} \dots \overline{R} \hat{x}_n \overline{R} \hat{y}$ where $\overline{\mathcal{M}}, \hat{x} \models \Box \varphi$, then
  $\overline{\mathcal{M}}, \hat{x}_n \models \Box \varphi$.

  If $\hat{x}_n \overline{R} \hat{y}$,
  then there are $x_n' \in \hat{x}_n$ and  $y' \in \hat{y}$ with $x_n' R y'$. $\mathcal{M}, x_n' \models \Box \varphi$ implies $\mathcal{M}, y' \models \varphi$, but $y'$ and $y$ are $\Gamma$-equivalent and $\varphi \in \Gamma$, so $\mathcal{M}, y \models \varphi$.
\end{proof}

@@

\begin{lemma}
  Let $\mathcal{L}$ be a modal logic and $\varphi \not\in \mathcal{L}$, then $\mathcal{M}_{\mathcal{L}}^{\operatorname{Sub}(\varphi)} \nvDash \varphi$.
\end{lemma}

\begin{theorem} $\mathcal{L}$ be a modal logic, then the following are equivalent:
  \begin{enumerate}
    \item $\mathcal{L}$ admits strict filtrations
    \item If $\Gamma$ is a finite $\operatorname{Sub}$-closed set of formulas , there exists a finite ``canonical'' model $\mathcal{M}_{\mathcal{L}}^{\Gamma}$ such that
    $\mathcal{M}_{\mathcal{L}}^{\Gamma} \models \mathcal{L}$.
  \end{enumerate}
\end{theorem}

  \begin{enumerate}
    \item $(\Rightarrow)$
  Let $\Gamma$ be a finite $\operatorname{Sub}$-closed of formulas. $\mathcal{L}$ admits strict filtrations, so the filtration of the canonical model $\mathcal{M}_{\mathcal{L}}$ through $\Gamma$ is also an $\mathcal{L}$-model. The underlying set of $\mathcal{M}_{\mathcal{L}} / \sim_{\Gamma}$ consists of maximal $\mathcal{L}$ theories up to $\Gamma$-equivalence and this quotient set is finite.

  It is readily checked that the quotient model $\mathcal{M}_{\mathcal{L}} / \sim_{\Gamma}$ satifsfies Definition~\ref{fin}.

    \item $(\Leftarrow)$

    Let $\Gamma$ be a finite $\operatorname{Sub}$-closed of formulas and $\mathcal{M}_{\mathcal{L}}^{\Gamma} = \langle W_{\mathcal{L}}^{\Gamma}, R_{\mathcal{L}}^{\Gamma}, \vartheta_{\mathcal{L}}^{\Gamma} \rangle$ a ``finite canonical'' model generated by $\Gamma$.

    Let us show that there exists a model $\widehat{\mathcal{M}}$ such that
    $\widehat{\mathcal{M}}$ is a strict filtration of $\mathcal{M}$ through $\operatorname{Sub}(\Gamma)$.

    Let $\sim$ be an equivalence relation on $\underline{\mathcal{M}}$ defined as usual:

    \begin{center}
      $u \sim v$ iff $\forall \psi \in \Gamma$
      $\mathcal{M}, u \models \psi \Leftrightarrow \mathcal{M}, v \models \psi$
    \end{center}

    Let $[u] \in \mathcal{M}/\sim$, consider its truth set $||[u]|| = \{ \psi \in \Gamma \: | \: \mathcal{M}, u \models \psi \}$.
    $||[u]||$ is clearly a finite $\mathcal{L}$-consistent set and it is maximal.
    Consider a map
    \begin{center}
    $\iota : W/\sim \to W_{\mathcal{L}}^{\varphi}$ with $\iota : [u] \mapsto ||[u]||$
    \end{center}

    Consider the set $\iota(W/\sim)$ that we denote as $\operatorname{Im}(\iota)$. Let us show that $\operatorname{Im}(\iota)$ is $R_{\mathcal{L}}^{\varphi}$-closed.

    Let $\iota([u]) R_{\mathcal{L}}^{\varphi} \Delta$, let us show that $\Delta \in \iota(W/\sim)$, that is, $\Delta = \iota([v])$ for some $v \in W$.

@@

    Suppose that there are $u' \in [u]$ and $v' \in [v]$ with $u' R v'$. Let us show that
    $[u] \widehat{R} [v]$. That is, let us show that $\Diamond \iota(v) \subseteq \iota(v)$.
    But if $\mathcal{M}, v' \models \psi$ for $\Diamond \psi \in \Gamma$, then
    $\mathcal{M}, u' \models \Diamond \psi$. Recall that $u' \sim u$ and $v' \sim v$, so we have $\Diamond ||[v]|| \subseteq ||[u]||$.

    The second inclusion follows from the definition of a relation in a finite ``canonical'' model.
  \end{enumerate}
\end{proof}

In particular, ${\bf K}5$ fails to have the finite ``canonical'' model property that
follows from the contraposition of the theorem above and Theorem~\ref{sad}.

>>>>

\author{Daniel Rogozin}
\date{}
\title{Notes on filtration of logics containing {\bf K5}}
\begin{document}

@@

@@

\begin{enumerate}
  \item Let $\mathcal{L}$ be a complete normal modal logic. If $\operatorname{Frames}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property.
  \item If the class of models $\operatorname{Mod}(\mathcal{L})$ admits filtration, then $\mathcal{L}$ has the finite model property and it is Kripke complete as well.
\end{enumerate}
\end{lemma}

@@

  \xymatrix{
  &&&&&&& w_5\ar@(ul,ur) \ar@<-.5ex>[d] \\
  &&&&&& w_1\ar@(ul,ur)  & w_4 \ar@<.5ex>[u] \ar@(dl,ul)^{} \\
  &&&&&& w_2 \ar[u] & w_3 \ar[u]
  }
\end{proof}

@@

Let us also note that strict filtrations of this model is not Euclidean.
Suppose by contrary that $\widehat{R}^{\mathcal{E}}$ is a strict filtraction of that model. So $R_{min}^E \subseteq \widehat{R}^{\mathcal{E}}$, since $R_{min}^E$ is the minimal Euclidean relation containing $R_{min}$. On the other hand, $R_{min}^E \not\subseteq R_{max}$, so is not $\widehat{R}^{\mathcal{E}}$.

@@

\begin{lemma}\label{good}
  Let $\mathcal{L}$ be a modal logic and $\varphi \not\in \mathcal{L}$, then $\mathcal{M}_{\mathcal{L}}^{\operatorname{Sub}(\varphi)} \nvDash \varphi$.
\end{lemma}

\begin{lemma} Let $\mathcal{L}$ be a modal logic and $\Gamma$ a finite $\operatorname{Sub}$-closed set of formulas, then if $\mathcal{L}$ admits strict filtrations, then there exists a finite ``canonical'' model $\mathcal{M}_{\mathcal{L}}^{\Gamma}$ such that $\mathcal{M}_{\mathcal{L}}^{\Gamma} \models \mathcal{L}$.
\end{lemma}

\begin{proof}
  $ $
$(\Rightarrow)$
  Let $\Gamma$ be a finite $\operatorname{Sub}$-closed of formulas. $\mathcal{L}$ admits strict filtrations, so the filtration of the canonical model $\mathcal{M}_{\mathcal{L}}$ through $\Gamma$ is also an $\mathcal{L}$-model. The underlying set of $\mathcal{M}_{\mathcal{L}} / \sim_{\Gamma}$ consists of maximal $\mathcal{L}$ theories up to $\Gamma$-equivalence and this quotient set is finite.

  It is readily checked that the quotient model $\mathcal{M}_{\mathcal{L}} / \sim_{\Gamma}$ satifsfies Definition~\ref{fin}.
\end{proof}

The converse implication does not have to true generally. We prove a bit more weak version of this implication. A logic admits $\mathcal{L}$ admits $\Diamond$-filtrations, if for each model $\mathcal{M} \models \mathcal{L}$ and for each $\Gamma$, a $\operatorname{Sub}$-closed set of formulas, there exists a model $\widehat{\mathcal{M}}$, a filtration of $\mathcal{L}$ through $\operatorname{Sub}(\Gamma \cup \Diamond \Gamma)$.

${\bf K}5$ is an example of such a logic since ${\bf K}5$ admits filtrations through sets having the form $\Gamma \cup \{ \Diamond \Box \psi \: | \: \Box \psi \in \Gamma \}$.

Note that, if $\mathcal{L}$ admits $\Diamond$-filtrations, so $\mathcal{L}$ admits the ``finite canonical'' model property, the proof is the same as in Lemma~\ref{good}.

\begin{lemma}
  Let $\mathcal{L}$ be a logic that admits $\Diamond$-filtrations and $\Gamma$ a $\operatorname{Sub}$-closed set of formulas, then there exists a ``finite canonical'' model $\mathcal{M}^{\Gamma}_{\mathcal{L}} \models \mathcal{L}$
\end{lemma}

\begin{proof}
Let $\Gamma$ be a finite $\operatorname{Sub}$-closed of formulas and $\mathcal{M}_{\mathcal{L}}^{\Gamma} = \langle W_{\mathcal{L}}^{\Gamma}, R_{\mathcal{L}}^{\Gamma}, \vartheta_{\mathcal{L}}^{\Gamma} \rangle$ a ``finite canonical'' model generated by $\Gamma$.

Let us show that there exists a model $\widehat{\mathcal{M}}$, a strict filtration of $\mathcal{M}$ through $\operatorname{Sub}(\Gamma \cup \Diamond \Gamma) := \Psi$.

Let $\sim$ be an equivalence relation on $\mathcal{M}$ defined as usual:

    \begin{center}
      $u \sim v$ iff $\forall \psi \in \Psi$
      $\mathcal{M}, u \models \psi \Leftrightarrow \mathcal{M}, v \models \psi$
    \end{center}

    Let $[u] \in \mathcal{M}/\sim$, consider its truth set $||[u]|| = \{ \psi \in \Psi \: | \: \mathcal{M}, u \models \psi \}$.
    $||[u]||$ is clearly a finite $\mathcal{L}$-consistent set and it is maximal.
    Consider a map:
    \begin{center}
    $\iota : W/\sim \to W_{\mathcal{L}}^{\Gamma}$ with $\iota : [u] \mapsto ||[u]||$
    \end{center}

    Consider the set $\iota(W/\sim)$ that we denote as $\operatorname{Im}(\iota)$. Let us show that $\operatorname{Im}(\iota)$ is $R_{\mathcal{L}}^{\Gamma}$-closed.

    Let $\iota([u]) R_{\mathcal{L}}^{\Gamma} \Delta$, let us show that $\Delta \in \iota(W/\sim)$, that is, $\Delta = \iota([v])$ for some $v \in W$.

@@

    Suppose that there are $u' \in [u]$ and $v' \in [v]$ with $u' R v'$. Let us show that
    $[u] \widehat{R} [v]$. That is, let us show that $\Diamond \iota(v) \subseteq \iota(u)$.

    Suppose $\psi \in \iota(v)$, that is, $\psi \in ||v||$, that denotes $\psi \in \Psi$ and $\mathcal{M}, v \models \psi$. Therefore, $\mathcal{M}, v' \models \psi$. Then $\mathcal{M}, u' \models \Diamond \psi$. $\Diamond \psi \in \Psi$ and $u \sim_{\Gamma} u'$, so
    $\mathcal{M}, u \models \Diamond \psi$.

    The second inclusion follows from the definition of a relation in a finite ``canonical'' model.
\end{proof}

In particular, ${\bf K}5$ has the finite ``canonical'' model property.

### 2021-04-17 frp-paper/Paper.tex
New file with filtrations stuff

Let $\mathcal{A}$ be a join semilattice, a subset $I \subseteq \mathcal{A}$ is called \emph{ideal}, if the following hold:
\begin{enumerate}
  \item If $x \in I$, then $\down{x} \subseteq I$,
  \item $x, y \in I$ implies $x + y \in I$.
\end{enumerate}
The poset $\langle \operatorname{Id}(\mathcal{A}), \subseteq \rangle$ consists of all ideals of $\mathcal{A}$ ordered by inclusion. $\mathcal{A}$ a join semilattice is called \emph{distributive}, if for each $x, a, b \in \mathcal{A}$ such that $x \leq a + b$, so there are $a' \leq a$ and $b' \leq b$ such that $x = a' + b'$. A finite $\mathcal{A}$ is distributive is the lattice $\operatorname{Id}(\mathcal{A})$ is distributive in the usual sense, see \cite[Lemma 184]{gratzer2011lattice}.

>>>>

Let $\mathcal{A}$ be a join semilattice, a subset $I \subseteq \mathcal{A}$ is called \emph{ideal}, if the following hold:
\begin{enumerate}
  \item If $x \in I$, then $\down{x} \subseteq I$,
  \item $x, y \in I$ implies $x + y \in I$.
\end{enumerate}
The poset $\langle \operatorname{Id}(\mathcal{A}), \subseteq \rangle$ consists of all ideals of $\mathcal{A}$ ordered by inclusion. A join semilattice $\mathcal{A}$ is called \emph{distributive}, if for each $x, a, b \in \mathcal{A}$ such that $x \leq a + b$, so there are $a' \leq a$ and $b' \leq b$ such that $x = a' + b'$. A finite $\mathcal{A}$ is distributive is the lattice $\operatorname{Id}(\mathcal{A})$ is distributive in the usual sense, see \cite[Lemma 184]{gratzer2011lattice}.
